Generating Correlated Data for Omics Simulation

### 2025-08-05 manuscript/paper.qmd
Tweak wording

Other Gaussian copula-based R packages include `copula`, `bindata`, `GenOrd`, and `SimMultiCorrData`, the last of these being the most comprehensive.
The `bigsimr` package provides faster implementations of these methods which scale up to omics-level data.
However, even this is computationally demanding; their paper references generating 20,000-dimensional vectors in “under an hour” using 16 threads.
All of these packages provide more flexibility in specifying dependence and therefore the longer run-times may be unavoidable for use cases where researchers need to parameterize the dependence structure.
Another package that optimizes the speed of random multivariate normal vector generation is the `mvnfast` package for R [@mvnfast], however, we show that this does not provide a meaningful speedup for our use-cases due to the reliance on the Cholesky decomposition, see @fig-intro d.

>>>>

Other Gaussian copula-based R packages include `copula`, `bindata`, `GenOrd`, and `SimMultiCorrData`, the last of these being the most comprehensive.
The `bigsimr` package provides faster implementations of these methods which scale up to omics-level data.
However, even this is computationally demanding; their paper references generating 20,000-dimensional vectors in “under an hour” using 16 threads.
All of these packages provide more flexibility in specifying dependence and therefore the longer run-times may be unavoidable for use cases where researchers need to parameterize the dependence structure.
Another package that optimizes the speed of random multivariate normal vector generation is the `mvnfast` package for R [@mvnfast], however, we show that this does not provide a meaningful speedup for our use-cases, likely due to the reliance on the Cholesky decomposition, see @fig-intro d.
